Flatiron cleaning

### 2021-10-27 Rmd/rdi analysis adjusted weight.Rmd
Adding cleanup for cycle number and more

```{r}
therapy_line %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(had_neo, had_adj, therapy) %>% 
  tbl_summary(by = therapy,
              type = list(had_neo ~ "dichotomous", 
                          had_adj ~ "dichotomous"),
              missing = "no")
therapy_line %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(therapy, treatment_sequence) %>% 
  tbl_summary(by = therapy)
```

@@

First table is frontline Neo, second table is frontline Adj.
```{r}
therapy_line %>% 
  filter(linenumber == 1
         ) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

therapy_line %>% 
  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

@@

### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line
```{r Number of patient who switch line}
therapy_line %>% 
  mutate(change_line = case_when(
    linenumber == 1 & 
      linenumber_new == 2 &
      chemotherapy_type == "Adjuvant" &
      therapy == "Upfront Chemo"                   ~ 1,
    TRUE                                           ~ 0
  )) %>% 
  arrange(desc(change_line)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(change_line) %>% 
  tbl_summary()
```

For these patients, I was worried that the part of their first line which was switched to Adjuvant line because of surgery is short... How long is this adjuvant line?
```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, linenumber, linenumber_new, linenumber_adj, 
         drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= line_duration))+
  geom_histogram(color = "slateblue", fill = "grey", binwidth = 7) +
  theme_minimal(base_size = 14)+
  labs(x="Line duration", 
       y="Number of Patient",
       caption = "Each bar represents 7 days, bottom plot is zoomed in")+
  ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)

@@

```{r}
therapy_line %>% 
  mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
           duration(n = 1, units = "days")) %>% 
  filter(linenumber == 1 & linenumber_new == 2) %>% 
  select(patientid, drugname, episodedate, line_duration, 
         chemotherapy_type, therapy, 
         linenumber, linenumber_new, linenumber_adj) %>% 
  filter(line_duration < 30)
```

@@

```{r plot interval}
Treatment %>% 
  ggplot(aes(x= interval_creat)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_height)) +
#   geom_bar() +
#   coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_weight)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_bsa)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
Treatment %>% 
  ggplot(aes(x= interval_auc)) +
  geom_bar() #+
  # coord_cartesian(ylim=c(0,50))
```

@@

### Number of line in treatment and cycle in frontline  
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(cycle_increment) %>% 
  tbl_summary()
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Don't forget we have that "neo + surg"
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
  filter(linenumber_new == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront surgery
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  arrange(desc(linenumber_adj)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(linenumber_adj) %>% 
  tbl_summary()

Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  filter(linenumber_adj == 1) %>% 
  mutate(cycle_increment = factor(cycle_increment)) %>% 
  arrange(desc(cycle_increment)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(cycle_increment) %>% 
  tbl_summary()
```
<br>

## Missingness
Here some representation of missingness in our data:  
- In the first plot (horizontal bar), `r is.na(Frontline$height_at_dx) %>% sum()` data is missing for height closest to dx but `r Frontline %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx). Because these parameters overlap only 25 patients will have missing value for all of them.   
- In the second plot (horizontal bar), `r is.na(Frontline$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(Frontline$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation). the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose.
```{r}
library(naniar)
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
  gg_miss_upset()

Frontline %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
  gg_miss_upset()

>>>>

```{r}
# therapy_line %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(had_neo, had_adj, therapy) %>% 
#   tbl_summary(by = therapy,
#               type = list(had_neo ~ "dichotomous", 
#                           had_adj ~ "dichotomous"),
#               missing = "no")
# therapy_line %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(therapy, treatment_sequence) %>% 
#   tbl_summary(by = therapy)
```

@@

First table is frontline Neo, second table is frontline Adj.
```{r}
# therapy_line %>% 
#   filter(linenumber == 1
#          ) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))
# 
# therapy_line %>% 
#   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))

@@

### Number of patient who switch line because of surgery from line 1 neoadjuvant to an adjuvant line
```{r Number of patient who switch line}
# therapy_line %>% 
#   mutate(change_line = case_when(
#     linenumber == 1 & 
#       linenumber_new == 2 &
#       chemotherapy_type == "Adjuvant" &
#       therapy == "Upfront Chemo"                   ~ 1,
#     TRUE                                           ~ 0
#   )) %>% 
#   arrange(desc(change_line)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(change_line) %>% 
#   tbl_summary()
```

For these patients, I was worried that the part of their first line which was switched to Adjuvant line because of surgery is short... How long is this adjuvant line?
```{r}
# therapy_line %>% 
#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
#            duration(n = 1, units = "days")) %>% 
#   filter(linenumber == 1 & linenumber_new == 2) %>% 
#   select(patientid, linenumber, linenumber_new, linenumber_adj, 
#          drugname, chemotherapy_type, therapy, episodedate, line_duration) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   ggplot(aes(x= line_duration))+
#   geom_histogram(color = "slateblue", fill = "grey", binwidth = 7) +
#   theme_minimal(base_size = 14)+
#   labs(x="Line duration", 
#        y="Number of Patient",
#        caption = "Each bar represents 7 days, bottom plot is zoomed in")+
#   ggforce::facet_zoom(xlim = c(0, 100), zoom.size = 1)

@@

```{r}
# therapy_line %>% 
#   mutate(line_duration = interval(start = linestartdate_new, end = lineenddate_new)/ 
#            duration(n = 1, units = "days")) %>% 
#   filter(linenumber == 1 & linenumber_new == 2) %>% 
#   select(patientid, drugname, episodedate, line_duration, 
#          chemotherapy_type, therapy, 
#          linenumber, linenumber_new, linenumber_adj) %>% 
#   filter(line_duration < 30)
```

@@

```{r plot interval}
# Treatment %>% 
#   ggplot(aes(x= interval_creat)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# # Treatment %>% 
# #   ggplot(aes(x= interval_height)) +
# #   geom_bar() +
# #   coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_weight)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_bsa)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
# Treatment %>% 
#   ggplot(aes(x= interval_auc)) +
#   geom_bar() #+
#   # coord_cartesian(ylim=c(0,50))
```

@@

### Number of line in treatment and cycle in frontline  
Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)  
in upfront neo
```{r}
# Treatment %>% 
#   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
#   arrange(desc(linenumber_new)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linenumber_new) %>% 
#   tbl_summary()
# Treatment %>% 
#   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
#   filter(linenumber_new == 1) %>% 
#   mutate(cycle_increment = factor(cycle_increment)) %>% 
#   arrange(desc(cycle_increment)) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(cycle_increment) %>% 
#   tbl_summary()
# Treatment %>% 
#   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg + adj") %>% 
#   filter(linenumber_new == 1) %>% 
#   arrange(desc(cycle_increment)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(cycle_increment) %>% 
#   tbl_summary()
```
<!-- Don't forget we have that "neo + surg" -->
```{r}
# Treatment %>% 
#   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
#   filter(linenumber_new == 1) %>% 
#   arrange(desc(linenumber_new)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linenumber_new) %>% 
#   tbl_summary()
# 
# Treatment %>% 
#   filter(chemotherapy_type == "Neoadjuvant" & treatment_sequence == "neo + surg") %>% 
#   filter(linenumber_new == 1) %>% 
#   mutate(cycle_increment = factor(cycle_increment)) %>% 
#   arrange(desc(cycle_increment)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(cycle_increment) %>% 
#   tbl_summary()
```
<!-- Number of Adjuvant line in patients with upfront neo -->
```{r}
# Treatment %>% 
#   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
#   arrange(desc(linenumber_adj)) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(linenumber_adj) %>% 
#   tbl_summary()
# 
# Treatment %>% 
#   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
#   filter(linenumber_adj == 1) %>% 
#   mutate(cycle_increment = factor(cycle_increment)) %>% 
#   arrange(desc(cycle_increment)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(cycle_increment) %>% 
#   tbl_summary()
```
<!-- Number of Adjuvant line in patients with upfront surgery -->
```{r}
# Treatment %>% 
#   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
#   arrange(desc(linenumber_adj)) %>%
#   distinct(patientid, .keep_all = TRUE) %>%
#   select(linenumber_adj) %>% 
#   tbl_summary()
# 
# Treatment %>% 
#   filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
#   filter(linenumber_adj == 1) %>% 
#   mutate(cycle_increment = factor(cycle_increment)) %>% 
#   arrange(desc(cycle_increment)) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(cycle_increment) %>% 
#   tbl_summary()
```
<br>

<!-- ## Missingness -->
<!-- Here some representation of missingness in our data:   -->
<!-- - In the first plot (horizontal bar), `r is.na(Frontline$height_at_dx) %>% sum()` data is missing for height closest to dx but `r Frontline %>% filter(is.na(weight_at_dx)) %>% distinct(patientid) %>% nrow()` is missing for weight  at dx (consequently bmi and bsa  at dx). Because these parameters overlap only 25 patients will have missing value for all of them.    -->
<!-- - In the second plot (horizontal bar), `r is.na(Frontline$CrCl) %>% sum()` data is missing for creatinine clearance, `r is.na(Frontline$target_auc) %>% sum()` data is missing for the taget_auc (hold on to the thought that this parameter include the target AUC calculated for Carboplatin and target dose calculated for cisplatin and taxanes, they are just present in the same column for a tidy data organisation). the vertical bar show that 413 info are missing for the intersection of the 4 parameters creatinine + creatinine clearance + target_auc + expected dose. -->
```{r}
# library(naniar)
# Frontline %>%
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(bmi_at_dx, weight_at_dx, height_at_dx, bsa_at_dx) %>% 
#   gg_miss_upset()
# 
# Frontline %>% select(creatinine, CrCl, target_auc, expected_dose) %>% 
#   gg_miss_upset()
